### 2019-03-27 _publications/jors/paper.tex
Changes for @amjokisaari

Generally, small scientific communities do not have the resources to
build and host dedicated web infrastructure to support their varied
content and data requirements. In particular, hosting and supporting a
complex content management system (CMS) including web servers, web
frameworks and databases requires a great deal of configuration and
long term support and funding. Furthermore, a turnkey CMS solution may
not meet requirements for a particular scientific group that may
require arcane data formats, custom data displays and client-side
automation. The PFHub effort, instead of focusing on the CMS tool,
focuses on customizing and delivering the client-side requirements
whilst delegating back-end functionality to external services that
provide dependable APIs~\cite{cmsfree}.

@@

The PFHub website provides a facility for uploading, displaying and
comparing results from the benchmark problems. The website uses the
Jekyll static website generator~\cite{jekyll} along with automated
front-end processing to eliminate the need for a CMS~\cite{cmsfree},
which are generally costly to maintain especially for small scientific
communities with limited funding and staffing.

@@

\begin{itemize}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.}, Figshare~\footnote{Certain
      commercial equipment, instruments, or materials (or suppliers,
      or software, ...) are identified in this paper to foster
      understanding. Such identification does not imply recommendation
      or endorsement by the National Institute of Standards and
      Technology, nor does it imply that the materials or equipment
      identified are necessarily the best available for the
      purpose.\label{disclaimer}}) configured with permissive
    cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

@@

The benchmark specifications consist of equations, narrative, plots
and code samples, and are composed in Jupyter Notebooks. The Jupyter
Notebooks are included as static objects in the website after
translation into HTML using the nbconvert tool~\cite{jupyter}.

The combination of a central repository on GitHub for website source
code and metadata with distributed data records on third-party
archives avoids the complexity and administrative overhead of
maintaining a live database and associated back-end application. The
PFHub infrastructure provides a template for other small scientific
communities to host custom content and integrate data from members of
their community.

@@

The framework has a fully automated test recipe deployed on Travis CI
with an environment built using the Nix Package
Manager~\cite{nix}. The environment is pinned to a specific version of
the Nixpkgs repository ensuring fully reproducible build and test
phases as well as ensuring that the development and automated testing
environments are identical. The full test recipe is outlined in a
\texttt{.travis.yml} file stored in the repository~\cite{travisyml}
and consists of the following steps.

@@

The PFHub framework can be deployed on any platform supporting Nix,
which includes all contemporary Linux and Mac OS X platforms. Since
the framework is built with Jekyll and automated front-end processing,
it can be deployed on GitHub's Pages infrastructure, which enables
streamlined deployment without the need for any back-end
infrastructure.

@@

\begin{itemize}
  \item Upload new benchmark definitions in a format that Jekyll can
    parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}

>>>>

Generally, small scientific communities do not have the resources to
build and host dedicated web infrastructure to support their varied
content and data requirements. In particular, hosting and supporting a
complex content management system (CMS) including web servers, web
frameworks and databases requires a great deal of configuration and
long term support and funding. Furthermore, a turnkey CMS solution may
not meet requirements for most scientific communities that often use
arcane data formats and require custom data displays along with
client-side automation. The PFHub effort, instead of focusing on the
CMS tool, focuses on customizing and delivering the client-side
requirements whilst delegating back-end functionality to external
services that provide dependable APIs~\cite{cmsfree}.

@@

The PFHub framework provides a template for other small scientific
communities to host custom content and integrate data from members of
their community. The current deployment provides a facility for
uploading, displaying and comparing results from benchmark problems
supporting phase-field code developers and practitioners. However, the
framework and overall philosophy are broadly transferable to other
communities with some custom configuration and content generation. The
framework uses the Jekyll~\cite{jekyll} static website
generator~\cite{jekyll} along with automated front-end processing to
eliminate the need for a CMS~\cite{cmsfree}, which is generally costly
to maintain especially for small scientific communities with limited
funding and staffing.

@@

\begin{itemize}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.},
    Figshare~\cite{figshare}~\footnote{Certain commercial equipment,
      instruments, or materials (or suppliers, or software, ...) are
      identified in this paper to foster understanding. Such
      identification does not imply recommendation or endorsement by
      the National Institute of Standards and Technology, nor does it
      imply that the materials or equipment identified are necessarily
      the best available for the purpose.\label{disclaimer}})
    configured with permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

@@

The current deployment of PFHub has benchmark specifications
consisting of equations, narrative, plots and code samples, and are
composed in Jupyter Notebooks. The Jupyter Notebooks are included as
static objects in the website after translation into HTML using the
nbconvert tool~\cite{jupyter}. There are currently 7 benchmark
problems each with a number of variations. At the time of writing
there are 108 separate benchmark result uploads~\cite{pfhub}, which
have all been approved via pull-request for compatibility with the
website.

The combination of a central repository on GitHub for website source
code and metadata with distributed data records on third-party
archives avoids the complexity and administrative overhead of
maintaining a live database and associated back-end application.

@@

The framework has a fully automated test recipe deployed on Travis CI
with an environment built using the Nix Package Manager~\cite{nix}. A
fully automated test environment using continuous integration allows
all developers and users to have common feedback on code updates and
determine the compatibility of result uploads with the deployed
website. The environment is pinned to a specific version of the
Nixpkgs repository ensuring fully reproducible build and test phases
as well as ensuring that the development and automated testing
environments are identical. The full test recipe is outlined in a
\texttt{.travis.yml} file stored in the repository~\cite{travisyml}
and consists of the following steps.

@@

The PFHub framework can be deployed on any platform supporting Nix,
which includes all contemporary Linux and Mac OS X platforms. Since
the framework is built with Jekyll and automated front-end processing,
it can be deployed on GitHub's Pages infrastructure, which enables
streamlined deployment without the need for any back-end
infrastructure and, thus, largely platform independent. For
development purposes, a Nix installation is required or use of the
supplied Docker container if using Windows.

@@

\begin{itemize}
  \item Upload new data upload specficiations (e.g. the phase-field
    benchmarks in the PFHub website~\cite{pfhub}) in a format that
    Jekyll can parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}
